% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Work Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Apr 2025}   {Research Intern}{SINTEF}{Oslo, Norway}
    {Sep 2025} {
                      \begin{itemize}
                        \item Advanced the SINDIT Digital Twin by extending its knowledge-graph schema and improving interoperability across sensor streams, asset metadata, and system ontologies.
                        \item Implemented a web-based interface for real-time visualization and interaction with the digital twin platform using SvelteKit and D3.js.
                        \item Designed and built an LLM-enhanced multi-agent architecture enabling real-time monitoring, contextual retrieval, and explainable human-in-the-loop assistance on live factory data.
                      \end{itemize}
                    }
                    {Knowledge Graphs,Neo4j,GraphDB,SvelteKit,d3.js,RAG,LangChain,LLMs,Multi-Agent Systems}
  \emptySeparator
  \experience
    {Apr 2022} {Analytics Project Manager \& Data Analyst}{Fossil Group Inc.}{Ho Chi Minh City, Vietnam}
    {Sep 2023}    {
                      \begin{itemize}
                        \item Promoted and held a dual role as Analytics Project Manager and Data Analyst in the 2nd year.
                        \item Planned sprint resources, timelines, and schedules for the analytics section in internal program release.
                        \item Led cross-functional teams to develop an A/B testing workflow for wearable devices and companion apps (experiment design, wireframes, rollout).
                        \item Implemented metrics frameworks and dynamic dashboards to track KPIs and gain valuable insights into user behavior, device performance monitoring, and wellness data from wearable devices.
                        \item Designed event tracking and data flows between IoT devices and apps.
                        \item Developed an internal Tracking Event Management tools for Data Quality Monitoring and Self-service Analytics, which automates the generation of daily queries and implements result alerts.
                      \end{itemize}
                    }
                    {BigQuery,Python,Looker,Tableau,AWS,IoT,Wearable Devices,A/B Testing,Project Management,Agile}
  \emptySeparator
  \experience
    {Aug 2021}     {Data Analyst}{Amanotes}{Ho Chi Minh City, Vietnam}
    {Feb 2022}    {
                      \begin{itemize}
                          \item Performed statistical and analytical analyses, including correlation between app events, A/B testing, cohort analysis, and aha-moment identification in the music game.
                          \item Built and maintained data pipelines with automated tests.
                          \item Implemented and analyzed spectrograms of musical notes of another instrument.
                          \item Trained and optimized TensorFlow Lite models for mobile inference.
                      \end{itemize}
                    }
                    {BigQuery,Airflow,dbt,TensorFlow,Python} 
  \emptySeparator
  \experience
  {Mar 2020}  {Software Engineer, Data}{Bosch Global Software Technologies}{Ho Chi Minh City, Vietnam}
  {Aug 2021}   {
                      \begin{itemize}
                          \item Collaborated with Bosch Automotive Products on automated driving use cases and data quality.
                          \item Analyzed software development logs and automotive radar data against QA/validation metrics for Advanced Driver Assistance Systems and Automotive Software Development Validation.
                          \item Built and maintained analytics CI pipelines in Jenkins (automated jobs, scheduled reporting).
                          \item Developed and operated data pipelines, databases, and dashboards for engineering stakeholders.
                          \item Implemented automated database deployment and dashboard releases to validation workflows.
                      \end{itemize}
                  }
                  {Jenkins,SQL,Python,Power BI,CI/CD,ADAS}
\end{experiences} 
